Asimilación de distintas observaciones

### 2021-01-22 analysis/chapters/experimento_20181122.Rmd
Fix cotours V-diff

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1.6, 1.2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-7, 0, 1), size = 0.2, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-7, 0, 1), color = "grey30", skip = 1, 
                    size = 4, stroke = 0.1) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r summary, fig.height=12, fig.width=10}
files <- Sys.glob(paste0(derived_data, "pw/*")) 
files <- files[!str_detect(files, c("E3"))]

@@

ana[bottom_top %between% c(1, 10), .(v_mean = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlGn", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(v_mean))),
                proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10)) +
   geom_text_contour(aes(z = v_mean), size = 4, stroke = 0.05,
                     proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10),
                label.placement = label_placement_n(1)) +
  scale_linetype(guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

ana[bottom_top %between% c(2, 10), .(theta_mean = mean(theta)), 
  by = .(south_north, west_east, date, exp)] %>% 
   .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
 # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = theta_mean, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7,
                    breaks = c(-Inf, seq(290, 314, 2), Inf), limits = c(-Inf, Inf)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "RdYlBu", direction = -1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

mucape %>% 
  .[variable == "mcape"] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  .[cor, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)), 
                    proj = norargentina_lambert, limits = c(500, 6000)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  # geom_contour2(aes(z = cortante),
  #               proj = norargentina_lambert, color = "black", size = 0.4,
  #               breaks = c(10, 25)) +
  geom_point(data = ~.x[cortante >= 10 & is.cross(x, y, skip = 1)], 
             aes(x = lon, y = lat, 
                 alpha = factor(cut_round(cortante, breaks = c(5, 15, 40)))),
             size = 0.00002, shape = 20) +
  scale_alpha_manual(values = c(0.3, 0.7), guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

@@

ana[west_east %between% c(70, 180)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  coord[., on = "south_north"] %>% 
  ggplot(aes(lat, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(..level..))), 
               color = "grey30", size = 0.3, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", 
                    size = 3, stroke = 0.05, breaks = seq(-10, 6, 2)) +
  scale_linetype(guide = NULL) +
  scale_x_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap( ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                     E6 = "SATWND", E7 = "RAD"))) +
  labs(y =  "Sigma levels", x = "Grid points") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) 
```

@@

```
```{r omb-t, fig.cap="Observation minus guess for humidity surface observations during Nov, 21st 18Z"}

@@

readRDS("/home/paola.corrales/mesoda/analysis/data/derived_data/IMERG_1h.rds") %>% 
  .[, c("lon", "lat") := wrf_project(x, y, inverse = TRUE, round = FALSE)] %>% 
  .[x %between% c(-300000, 800000) & y %between% c(-800000, 1090000)] %>% 
  .[end_date %between% c(as_datetime("20181120190000"), as_datetime("20181123120000"))] %>% 
  .[, .(pp_acum = mean(pp_acum),
        lat = mean(lat)), by = .(end_date, y)] %>% 
  ggplot(aes(end_date, lat)) +
  geom_contour2(aes(z = pp_acum, color = ..level..), 
               breaks = seq(1, 15, 1)) +
  scale_color_viridis_c(guide = NULL, breaks = seq(1, 14, 1), limits = c(1, 15)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  scale_y_latitude(breaks = seq(-40, -20, 5)) +
  labs(x = NULL, y = NULL, color = "PP acum", 
       subtitle = "IMERG") +
  theme_minimal() +
  theme(legend.position = "bottom") +

  ppacum_1h %>% 
  .[, lat := lat[1], by = .(y)] %>% 
  .[, .(pp_acum = mean(pp_acum)), by = .(exp, date, y, lat)] %>% 
  ggplot(aes(date, lat)) +
  # geom_raster(aes(fill = pp_acum)) +
  geom_contour2(aes(z = pp_acum, color = ..level..),
               breaks = seq(1, 15, 1)) +
  scale_color_viridis_c(breaks = seq(1, 15, 1), limits = c(1, 15),
                        guide = guide_colorstrip(inside = TRUE,
                                                 barwidth = 25,
                                                 barheight = 1)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  scale_y_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap(~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

@@

dbz %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barheight = 18)) +
  geom_mapa() +
  facet_grid(date~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal()
```

```{r dbz-ens}

@@

dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(cumulus, exp, date, lon, lat, x, y)] %>% 
  .[date == unique(date)[1]] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barheight = 18, 
                                           barwidth = 1)) +
  geom_mapa() +
  facet_grid(cumulus~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal()

  dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(cumulus, exp, date, lon, lat, x, y)] %>% 
  .[date == unique(date)[2]] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barheight = 18, barwidth = 1)) +
  geom_mapa() +
  facet_grid(cumulus~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal()

@@

sondeos %>% 
  .[, iop := fcase(launch_time %between% c(ymd_hms("20181121150000"), ymd_hms("20181121210000")), "IOP07",
                   launch_time %between% c(ymd_hms("20181122140000"), ymd_hms("20181122200000")), "IOP08")] %>% 
  .[variable %in% c("t", "td", "u", "v") & !str_detect(site, "/") & !is.na(fcst_value) & !is.na(iop)] %>% 
  .[, lev := cut_round(alt, seq(0, 20000, 1000))] %>% 
  .[, ":="(RMSE = mean(sqrt((value - fcst_value)^2)), 
           BIAS = mean(value - fcst_value)), by = .(iop, exp, variable, lev)] %>% 
  melt(measure.vars = c("RMSE", "BIAS"), variable.name = "estadistico", value.name = "value.est") %>% 
  ggplot(aes(lev/1000, value.est)) +
  geom_line(aes(color = exp, linetype = estadistico)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  coord_flip() +
  facet_grid(iop~variable, scales = "free_x") +
  labs(x = NULL, y = NULL, color = NULL, linetype = NULL) +
  theme_minimal()
```

>>>>

```{r V-diff, fig.cap="Meridial wind difference between experiments in m/s"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E4 = E5 - E4,
           E6_E5 = E6 - E5,
           E7_E6 = E7 - E6)] %>% 
  melt(measure.vars = c("E5_E4", "E6_E5", "E7_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.2, 0.2), Inf)) +
  scale_fill_divergent_discretised(name = NULL, limits = c(-1.6, 1.2),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 = E7)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-9, 0, 1), size = 0.2, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E4 = E5, E6_E5 = E6, E7_E6 =E7)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-9, 0, 1), color = "grey30", skip = 1, 
                    size = 4, stroke = 0.1) +
  labs(subtitle = "V difference (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, labeller = labeller(variable = c("E5_E4" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E7_E6" = "RAD - SATWND"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r summary, fig.height=10, fig.width=10}
files <- Sys.glob(paste0(derived_data, "pw/*")) 
files <- files[!str_detect(files, c("E3"))]

@@

ana[bottom_top %between% c(1, 10), .(v_mean = mean(v)), 
  by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlGn", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(v_mean))),
                proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10)) +
   geom_text_contour(aes(z = v_mean), size = 4, stroke = 0.05,
                     proj = norargentina_lambert, color = "darkorange", 
                breaks = c(-10, -5, -2, 0, 2, 5, 10),
                label.placement = label_placement_n(1)) +
  scale_linetype(guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

ana[bottom_top %between% c(2, 10), .(theta_mean = mean(theta)), 
  by = .(south_north, west_east, date, exp)] %>% 
   .[pw, on = .NATURAL] %>% 
ggplot(aes(x, y)) +
 # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = theta_mean, fill = stat(level_d)),
                    proj = norargentina_lambert, alpha = 0.7,
                    breaks = c(-Inf, seq(290, 314, 2), Inf), limits = c(-Inf, Inf)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "RdYlBu", direction = -1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

mucape %>% 
  .[variable == "mcape"] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  .[cor, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)), 
                    proj = norargentina_lambert, limits = c(500, 6000)) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  # geom_contour2(aes(z = cortante),
  #               proj = norargentina_lambert, color = "black", size = 0.4,
  #               breaks = c(10, 25)) +
  geom_point(data = ~.x[cortante >= 10 & is.cross(x, y, skip = 1)], 
             aes(x = lon, y = lat, 
                 alpha = factor(cut_round(cortante, breaks = c(5, 15, 40)))),
             size = 0.00002, shape = 20) +
  scale_alpha_manual(values = c(0.3, 0.7), guide = NULL) +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(1, 1, 1, 1),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

@@

ana[west_east %between% c(70, 180)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  coord[., on = "south_north"] %>% 
  ggplot(aes(lat, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(name = NULL, super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(..level..))), 
               color = "grey30", size = 0.3, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", 
                    size = 3, stroke = 0.05, breaks = seq(-10, 6, 2)) +
  scale_linetype(guide = NULL) +
  scale_x_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap( ~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                     E6 = "SATWND", E7 = "RAD"))) +
  labs(y =  "Sigma levels") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) 
```

@@

```{r omb-t, fig.cap="Observation minus guess for humidity surface observations during Nov, 21st 18Z"}

@@

readRDS("/home/paola.corrales/mesoda/analysis/data/derived_data/IMERG_1h.rds") %>% 
  .[, c("lon", "lat") := wrf_project(x, y, inverse = TRUE, round = FALSE)] %>% 
  .[x %between% c(-300000, 800000) & y %between% c(-800000, 1090000)] %>% 
  .[end_date %between% c(as_datetime("20181120190000"), as_datetime("20181123120000"))] %>% 
  .[, .(pp_acum = mean(pp_acum),
        lat = mean(lat),
        exp = "IMERG"), by = .(end_date, y)] %>% 
  ggplot(aes(end_date, lat)) +
  geom_contour2(aes(z = pp_acum, color = ..level..), 
               breaks = seq(1, 15, 1)) +
  scale_color_viridis_c(guide = NULL, breaks = seq(1, 14, 1), limits = c(1, 15)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  scale_y_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap(~ exp) +
  labs(x = NULL, y = NULL, color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

  ppacum_1h %>% 
  .[, lat := lat[1], by = .(y)] %>% 
  .[, .(pp_acum = mean(pp_acum)), by = .(exp, date, y, lat)] %>% 
  ggplot(aes(date, lat)) +
  # geom_raster(aes(fill = pp_acum)) +
  geom_contour2(aes(z = pp_acum, color = ..level..),
               breaks = seq(1, 15, 1)) +
  scale_color_viridis_c(breaks = seq(1, 15, 1), limits = c(1, 15),
                        guide = guide_colorstrip(inside = TRUE,
                                                 barwidth = 25,
                                                 barheight = 0.8)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  scale_y_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap(~ exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom") +

@@

dbz %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barwidth = 0.8, 
                                           barheight = 20)) +
  geom_mapa() +
  facet_grid(date~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

```{r dbz-ens, fig.height=10, fig.width=7}

@@

  dbz %>% 
  .[, .(max_dbz = mean(max_dbz, na.rm = TRUE)), by = .(cumulus, exp, date, lon, lat, x, y)] %>% 
    .[date %in% unique(date)[1:2]] %>% 
    .[, date := factor(date)] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = max_dbz, fill = stat(level_d)), 
                    proj = norargentina_lambert,
                    breaks = seq(0, 60, 5),) +
  scale_color_dbz(aesthetics = "fill", super = ScaleDiscretised, 
                  guide = guide_colorsteps(barheight = 0.8, 
                                           barwidth = 20)) +
  geom_mapa() +
  ggh4x::facet_nested(date + cumulus ~ exp, 
                      labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                                   E6 = "SATWND", E7 = "RAD"))) +
  labs(fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

sondeos %>% 
  .[, iop := fcase(launch_time %between% c(ymd_hms("20181121150000"), ymd_hms("20181121210000")), "IOP07",
                   launch_time %between% c(ymd_hms("20181122140000"), ymd_hms("20181122200000")), "IOP08")] %>% 
  .[variable %in% c("t", "td", "u", "v") & !str_detect(site, "/") & !is.na(fcst_value) & !is.na(iop)] %>% 
  .[, lev := cut_round(alt, seq(0, 20000, 1000))] %>% 
  .[, ":="(RMSE = mean(sqrt((value - fcst_value)^2), na.rm = TRUE), 
           BIAS = mean(value - fcst_value, na.rm = TRUE)), by = .(iop, exp, variable, lev)] %>% 
  melt(measure.vars = c("RMSE", "BIAS"), variable.name = "estadistico", value.name = "value.est") %>% 
  ggplot(aes(lev/1000, value.est)) +
  geom_hline(yintercept = 0, color = "grey30") +
  geom_line(aes(color = exp, linetype = estadistico)) +
  scale_color_manual(values = colores_exp, labels = c(E4 = "CONV", E5 = "AUT", 
                                                      E6 = "SATWND", E7 = "RAD")) +
  coord_flip() +
  facet_grid(iop~variable, scales = "free_x", 
             labeller = labeller(variable = c("t" = "Temperature",
                                              "td" = "Dew point\ntemperature",
                                              "u" = "U wind",
                                              "v" = "V wind"))) +
  labs(y = NULL, x = "Height (Km)", color = NULL, linetype = NULL) +
  theme_minimal()
```
